### 2014-06-01 ACL2014/system.tex
section 2 edits

Our aim is to empirically study a set of locality sensitive hashing techniques
that enable us to return a set of candidate neighbors while performing
a much smaller (theoretically \emph{sublinear}) set of comparisons.

The motivated behind this research is to find nearest neighbors by doing a 
\emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
In addition to \emph{small} number of comparisons, we also want to 
return a set of neighbor candidates with a $100\%$ precision and a large recall. 
The method we propose meet all these criterions. We do this by exploiting 
existing research in \lshf (a.k.a., \lsh) and propose their novel variants. 
In particular, we develop the framework of  \lsh algorithms on a distributed 
system (e.g. Hadoop) to take advantage of its computing efficiency.

>>>>

Our aim is to empirically study a set of locality sensitive hashing techniques
that enable us to return a set of candidate neighbors while performing
a much smaller (theoretically \emph{sublinear}) set of comparisons. 
In order to tackle this scalability problem, we explore the 
combination of distributed computation using a map-reduce platform (Hadoop) as well as
locality sensitive hashing (\lsh) algorithms. 
We explore a few commonly known variants of \lsh and suggest a few novel variants
that are suitable to the map-reduce platform. 
The methods that we propose meets the practical requirements of a real life 
search engine backend, and demonstrates how to use locality sensitive hashing
on a distributed platform.

% The motivated behind this research is to find nearest neighbors by doing a 
% \emph{small} number of comparisons (sublinear in dataset size), instead of brute force linear search. 
% In addition to \emph{small} number of comparisons, we also want to 
% return a set of neighbor candidates with a $100\%$ precision and a large recall. 
% The method we propose meet all these criterions. We do this by exploiting 
% existing research in \lshf (a.k.a., \lsh) and propose their novel variants. 
% In particular, we develop the framework of  \lsh algorithms on a distributed 
% system (e.g. Hadoop) to take advantage of its computing efficiency.
